Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
fix: 修正汉诺塔训练结果的描述

Action chunking mitigates error accumulation in long-horizon tasks~\cite{ref10}, the integrated task execution achieved a 60\% success rate (6/10) when sequentially deploying all models to complete the full Tower of Hanoi task.

@@

Figure~\ref{fig9} illustrates the entire task workflow. It begins with the global-view camera identifying the soiled plate. The blue robotic arm then moves to the plate's position and, guided by the mid-level camera, precisely grips the plate's edge. Next, the white robotic arm picks up the sponge and wipes the stains off the plate until the global-view camera confirms the plate is clean~\cite{fu_deep_2022}. The white arm then releases the sponge and returns to its initial position. Subsequently, the blue robotic arm, guided by the side-view camera, accurately places the cleaned plate onto the designated spot (marked with a red positioning tag) before resetting. This concludes the task.

>>>>

Action chunking mitigates error accumulation in long-horizon tasks by decomposing them into manageable units~\cite{ref10}. Experimental results demonstrate that while individual actions can achieve over 90\% success rate, the integrated task execution system's overall performance drops to 60\% (6/10) in sequential model deployment for the complete Tower of Hanoi task due to the bucket effect.

@@

\textbf{Figure~\ref{fig9}} illustrates the entire task workflow. It begins with the global-view camera identifying the soiled plate. The blue robotic arm then moves to the plate's position and, guided by the mid-level camera, precisely grips the plate's edge. Next, the white robotic arm picks up the sponge and wipes the stains off the plate until the global-view camera confirms the plate is clean~\cite{fu_deep_2022}. The white arm then releases the sponge and returns to its initial position. Subsequently, the blue robotic arm, guided by the side-view camera, accurately places the cleaned plate onto the designated spot (marked with a red positioning tag) before resetting. This concludes the task.
